---
title: "Telecom users dataset"
author: Kornel Olszewski
output:
html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

This project aims to provide model for data described in https://www.kaggle.com/radmirzosimov/telecom-users-dataset

# Environment setup

```{r}
library(tidyverse)
library(mlr3verse)
library(here)
library(vroom)
library(skimr)
library(DataExplorer)
```

# Data import

```{r}
tab = here("telecom-users-dataset","archive.zip") %>% vroom()
```

# Overview of data

```{r}
tab %>% glimpse()
```


```{r}
tab %>% skim()
```
The dataset consists of 17 character variables and 5 numeric variables. Out of them: *Churn* is the dependent variable and *customerID* is a case label, which will be skipped in computation. There is one variable - *TotalCharges* - which has missing values. Let's see what can be understood from data exploration.

# Initial data exploration

```{r, fig.width=14, fig.height=12}
plot_bar(tab, by = "Churn")
```

Upon first look it seems that there are little to no differences in distribution of dependent variable against *gender* and *Phone Service* within discrete variables. 

```{r, fig.width=12, fig.height=6}
tab %>% select(.,MonthlyCharges,tenure,TotalCharges) %>% plot_histogram()
```

*TotalCharges* seems to have lognormal distribution. Lets apply a *log* transformation and see what happens:

```{r, fig.width=12, fig.height=6}
tab %>% 
  select(.,TotalCharges) %>% 
  transmute(.,l_TotalCharges = log(TotalCharges + 1)) %>%
  plot_histogram()
```

The distribution is not quite similar to normal one, but looks better than the original. Let's check if there is correlation between independent variables:

```{r, fig.width=12, fig.height=12}
tab %>%
  mutate(.,l_TotalCharges = log(TotalCharges + 1)) %>%
  select(.,-c("...1", "Churn", "TotalCharges")) %>%
  na.omit() %>%
  plot_correlation(., type = "c")
```

Looks like *Tenure* and *l_TotalCharges* on one hand, and *MonthlyCharges* with *l_TotalCharges* are correlated. During modeling  it will be worthwhile to apply Principal Component Analysis to those pairs of variables. Let's see what it might look like:

```{r}
tab %>%
  mutate(.,l_TotalCharges = log(TotalCharges + 1)) %>%
  select(.,tenure,l_TotalCharges) %>%
  na.omit() %>%
  plot_prcomp()
```

```{r}
tab %>%
  mutate(.,l_TotalCharges = log(TotalCharges + 1)) %>%
  select(.,MonthlyCharges,l_TotalCharges) %>%
  na.omit() %>%
  plot_prcomp()
```

In case of the first pair one principal component based on two selected columns explains 92% of variance while with the second pair: 79%. 

# Initial modelling preparation



